%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]
\geometry{left=1cm, top=.8cm, right=1cm, bottom=1cm, footskip=.5cm}
\usepackage{hyperref}
%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{000000}
\definecolor{graytext}{HTML}{414141}
\definecolor{lighttext}{HTML}{414141}
\address{Calgary, Alberta}
\name {Mahmoud}{Abdelaty}
\mobile{(+1) 587-969-4502}
\email{mahmoud.abdelaty@ucalgary.ca}
\github{krang-8}
\linkedin{mahmoudabdelaty}



%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makecvheader[C]

	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5mm}
\cvsection{Education}
\begin{cventries}
    \vspace{-2mm}
	\cventry
	{University of Calgary}
	{Bachelor\textquotesingle{}s Degree in Computer Science}
	{Calgary, Alberta}
	{2019 – 2023}
    {
      \begin{cvparagraph} % Description(s) bullet points
        {Relevant Courses : CPSC for CPSC Majors I \& II, Principles of Microeconomics, Linear Methods , Calculus , Discrete Mathematics, Elementary Formal Logic, Statistics , Data Structures, Algorithms \& Analysis, Computing Machinery I \& II, Thinking with Data, Personal Financial Management, Computability, Intro to Software Engineering, Info Security \& Privacy, IT Ethics, Design \& Analysis Algorithms, Programming Paradigms, DBMS, HCI I \& II, Web-Based Systems.}
      \end{cvparagraph}
      }
     

%---------------------------------------------------------

\end{cventries}


\vspace{-11mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Project Experience}
\vspace{-4mm}
\begin{cventries}
	  \cventry
	{February 2022 - April 2022}
    {Agora}
	{NodeJS, React, ASP.Net, SQLite, CSS, HTML, Java, Swagger, Postman API}
	{\href{https://github.com/krang-8/Agora}{Github Repository}}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Lead a group of 3 to build a full-stack ecommerce store base and DBMS targeting small businesses.}
        \item {Used \textbf{Node.JS} and a \textbf{REACT }UI Frontend that communicated with an \textbf{ASP.NET Core V6 Minimal Web API} to perform CRUD operations.}
        \item {Utilized a \textbf{CODE-FIRST} approach to generate the database using \textbf{entity framework}.}
      \end{cvitems}
    }
    	\vspace{1mm}
    \vspace{-2mm}

		  \cventry
	{February 2020 - April 2020}
	{Cooks N Books}
	{C\#, WPF, XAML, CSS, Git }
	{\href{https://github.com/krang-8/cooksNbooks}{Github Repository}}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Identified work contexts, system constraints and expected users based on research conducted utilizing the task centered system design process.}
        \item {Designed paper prototypes and hand drawn sketches for the UI/UX.}
        \item {Utilized an agile workflow to keep track of progress and efficiently manage personnel}
        \item { Conducted an in-depth heuristics analysis on the final prototype identifying 29 heuristic problems with 5 
causing major usability problems.}
      \end{cvitems}
    }
        	\vspace{1mm}
	  \cventry
	{February 2021 - April 2021}
    {Self Checkout Station}
	{Java, JUnit}
	{\href{https://github.com/krang-8/SENG-300-Iteration-3}{Github Repository}}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Worked with a team of 12 members to develop a self checkout station system.}
        \item {Worked with the back-end team to implement key features for the checkout station.}
        \item {Co-lead the quality assurance team and built \textbf{JUnit} unit tests for the entire system ensuring a bug-free system.}
      \end{cvitems}
    }
    	\vspace{1mm}

	  \cventry
    {July 2020 - September 2020} 
    {Game Tracker Discord Bot}
    {Python, APIs, Digital Ocean} 
    {\href{https://github.com/krang-8/Game-Tracker}{Github Repository}} 
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Utilized both the discord and faceit apis to fetch, collect and post data based on live matches 24/7 and player statistics upon request.}
        \item {Hosted, deployed, and maintained for months on \textbf{DigitalOcean}.}
        \item {Optimized running time to \textbf{increase response time by 86.67\%}.}
      \end{cvitems}
    }


	
	
\cventry
	{February 2020 - April 2020}
	{Side Scroller Video Game}
	{Java, JavaFX}
	{\href{https://github.com/krang-8/Game-Project}{Github Repository}}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed and developed a side-scroller adventure video game utilizing \textbf{java} and \textbf{javafx} among a team of 4 where I created sprites for the character model and implemented a collision system to ensure smooth and seamless movement and interaction with the game world. }
      \end{cvitems}
    }

\end{cventries}


\vspace{-4mm}

\cvsection{Work Experience}
\vspace{-2mm}
\begin{cventries}
	\cventry
	{Automation Engineer (Internship)}
	{Royal Bank of Canada}
	{Remote in Calgary}
	{January 2023 - August 2023}
	{\begin{cvitems}
		\item {Automated compliance workflows using \textbf{Ansible playbooks} to parse \textbf{Tableau} views, clean data, identify compliance issues, and assign \textbf{JIRA} tickets, eliminating toil and improving efficiency across the bank.}
		\item {Developed an implementation for transaction monitoring on \textbf{MQ} channels through \textbf{Dynatrace}, enabling real-time tracking and performance using \textbf{Elastic}.}
		\item {Worked in an agile environment using \textbf{Jira} to keep track of tasks and progress in sprints and PIs and \textbf{Confluence} for documentation purposes.}
  		\item {Utilized \textbf{Docker, Jfrog Artifactory, Dynatrace, Moogsoft, Vault}, and the \textbf{ELK stack} following SRE principles and best practices, resulting in improved reliability,security, and accelerated development cycles, while increasing data observability.}
		\item {Designed and developed \textbf{self-healing token} capabilities on Ansible Tower.}
		\end{cvitems}}
		\vspace{1mm}
  
	\cventry
	{Data Analyst \& Junior Community Manager}
	{YaLLa Esports}
	{Dubai, UAE}
	{April 2021 – Present}
	{\begin{cvitems}
		\item {Co-lead the data analysis team compiling monthly, quarterly and campaign-focused data reports, in addition to competitors reports, evaluating technical and social aspects leading to a consistent increase in engagement, impressions and social growth.}
		\item {Assisted in growing the organization's social media channels by covering live games, generating content ideas, producing content, organizing community events, and communicating with the fans.}
  		\item {Utilized data analysis tools such as \textbf{Excel}, \textbf{Cavea} and \textbf{Tableau}.}
		\end{cvitems}}
		\vspace{1mm}
	\cventry
	{Head Admin}
	{Middle East Stars League}
	{Remote in Dubai}
	{April 2020 – November 2021}
	{\begin{cvitems}
		\item {Managed both daily operations and tournaments for a gaming hub helping it \textbf{grow tenfold} with over 12500 followers and 3000 paying active subscribers.}
		\item {Oversaw staff work and provided insight and assistance to new staff as well as handling staff applications and hiring new staff.}
		\end{cvitems}}

	\vspace{1mm}

	\cventry
	{Esports Admin - Observer - Event Organizer}
	{Freelance}
	{Dubai, UAE}
	{2020 – 2021}
	{\begin{cvitems}
 		\item {Worked with esports operators such as \textbf{PLG, Webedia, Saudi Esport Federation} to ensure and maintain contestants happiness and satisfaction through fair rulings and official communication for events sponsored by large brands such as \textbf{KFC, Adidas, Red Bull}.}
		\item {Coded scripts to \textbf{verify 5000+ contestant profiles} saving over \textbf{200+} hours of work for a 9-man admin team.}
		\item {Assisted in formulating storytelling narratives for the social media teams.}
		\end{cvitems}}
\end{cventries}



\ 
\end{document}
